Collaborative Visual Analysis on the Web with RCloud

### 2015-06-23 discussion.tex
table 1 rework
update

\begin{table*}
  \centering
  \begin{tabular}{l|cccccc}
           & Versioning/Forking & Collaboration & Deployment & Multilanguage & Integrated Reports & Integrated Analysis \\
    \hline
RCloud     &       x            &       x       &     x      &      x        &           x        &           x         \\
RStudio    &                    &               &            &               &           x        &           x         \\
JSFiddle   &       x            &       x       &            &               &                    &                     \\
bl.ocks    &       x            &       x       &            &               &           x        &                     \\
shiny      &                    &               &     x      &               &           x        &           x         \\
Jupyter    &                    &               &            &      x        &           x        &           x         \\
Tableau    &                     &      x        &    x       &               &          x         &                     
  \end{tabular}
  \caption{Comparison of system features.}
\end{table*}
% SN says Tableau: versioning=no  collaboration=yes  deployment=yes multilanguage=no  reports=yes  analysis=no

>>>>

\begin{table}
  \centering
  \begin{tabular}{l|cccccc}
    & V./F. & C. & D. & M.L. & R. & A. \\
    \hline
RCloud     &       x            &       x       &     x      &      x        &           x        &           x         \\
RStudio    &                    &               &            &               &           x        &           x         \\
JSFiddle   &       x            &       x       &            &               &                    &                     \\
bl.ocks    &       x            &       x       &            &               &           x        &                     \\
shiny      &                    &               &     x      &               &           x        &           x         \\
Jupyter    &                    &               &            &      x        &           x        &           x         \\
Tableau    &                    &      x        &     x      &               &           x        &                     \\
ManyEyes   &                    &      x        &     x      &               &                    &                     
  \end{tabular}
  \caption{Comparison of system features. Columns: Versioning/Forking, Collaboration, Deployment, Multi-language support, Integrated Reports, and Integrated Analysis.}
\end{table}
% SN says Tableau: versioning=no  collaboration=yes  deployment=yes multilanguage=no  reports=yes  analysis=no
